


Preguntar mario si va CFA aqui

### Stereotype content model: morality

```{r}
#| label: tbl-desc11
#| tbl-cap: "Descriptive statistics of Stereotype content model: morality"
#| tbl-cap-location: top

describe_kable(db_proc, c("mor_1", "mor_2", "mor_3"))

```

```{r}
#| collapse: false
# 1. Correlations ppw

# fit pearson and polychoric
res2 <- fit_correlations(db_proc, c("mor_1", "mor_2", "mor_3"))

```

```{r}
#| label: fig-15
#| fig-cap: "Correlation matrixes of Stereotype content model: morality"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "mor"
result2 <- alphas(db_proc, c("mor_1", "mor_2", "mor_3"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("mor_1", "mor_2", "mor_3")], na.rm = TRUE)
```

### Stereotype content model: warmth

```{r}
#| label: tbl-desc12
#| tbl-cap: "Descriptive statistics of Stereotype content model: warmth"
#| tbl-cap-location: top

describe_kable(db_proc, c("war_1", "war_2", "war_3"))

```

```{r}
#| collapse: false
# 1. Correlations ppw

# fit pearson and polychoric
res2 <- fit_correlations(db_proc, c("war_1", "war_2", "war_3"))

```

```{r}
#| label: fig-16
#| fig-cap: "Correlation matrixes of Stereotype content model: warmth"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "war"
result2 <- alphas(db_proc, c("war_1", "war_2", "war_3"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("war_1", "war_2", "war_3")], na.rm = TRUE)
```

Preguntar mario si va CFA aqui

### Stereotype content model: competence

```{r}
#| label: tbl-desc13
#| tbl-cap: "Descriptive statistics of Stereotype content model: competence"
#| tbl-cap-location: top

describe_kable(db_proc, c("com_1", "com_2", "com_3"))

```

```{r}
#| collapse: false
# 1. Correlations ppw

# fit pearson and polychoric
res2 <- fit_correlations(db_proc, c("com_1", "com_2", "com_3"))

```

```{r}
#| label: fig-17
#| fig-cap: "Correlation matrixes of Stereotype content model: competence"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "com"
result2 <- alphas(db_proc, c("com_1", "com_2", "com_3"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("com_1", "com_2", "com_3")], na.rm = TRUE)
```

Preguntar mario si va CFA aqui

### Intergroup behavioural tendencies: passive harm

```{r}
#| label: tbl-desc14
#| tbl-cap: "Descriptive statistics of Intergroup behavioural tendencies: passive harm"
#| tbl-cap-location: top

describe_kable(db_proc, c("ph_1", "ph_2"))

```

```{r}
#| collapse: false
# 1. Correlations ppw

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("ph_1", "ph_2"))

```

```{r}
#| label: fig-18
#| fig-cap: "Correlation matrixes of Intergroup behavioural tendencies: passive harm"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "ph"
result2 <- alphas(db_proc, c("ph_1", "ph_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("ph_1", "ph_2")], na.rm = TRUE)
```

Preguntar mario si va CFA aqui

### Intergroup behavioural tendencies: active harm

```{r}
#| label: tbl-desc15
#| tbl-cap: "Descriptive statistics of Intergroup behavioural tendencies: active harm"
#| tbl-cap-location: top

describe_kable(db_proc, c("ah_1", "ah_2"))

```

```{r}
#| collapse: false
# 1. Correlations ppw

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("ah_1", "ah_2"))

```

```{r}
#| label: fig-19
#| fig-cap: "Correlation matrixes of Intergroup behavioural tendencies: active harm"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "ah"
result2 <- alphas(db_proc, c("ah_1", "ah_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("ah_1", "ah_2")], na.rm = TRUE)
```

### Intergroup behavioural tendencies: passive facilitation

```{r}
#| label: tbl-desc16
#| tbl-cap: "Descriptive statistics of Intergroup behavioural tendencies: passive facilitation"
#| tbl-cap-location: top

describe_kable(db_proc, c("pf_1", "pf_2"))

```

```{r}
#| collapse: false
# 1. Correlations ppw

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("pf_1", "pf_2"))

```

```{r}
#| label: fig-20
#| fig-cap: "Correlation matrixes of Intergroup behavioural tendencies: passive facilitation"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "pf"
result2 <- alphas(db_proc, c("pf_1", "pf_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("pf_1", "pf_2")], na.rm = TRUE)
```

### Intergroup behavioural tendencies: active facilitation

```{r}
#| label: tbl-desc17
#| tbl-cap: "Descriptive statistics of Intergroup behavioural tendencies: active facilitation"
#| tbl-cap-location: top

describe_kable(db_proc, c("af_1", "af_2"))

```

```{r}
#| collapse: false
# 1. Correlations ppw

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("af_1", "af_2"))

```

```{r}
#| label: fig-21
#| fig-cap: "Correlation matrixes of Intergroup behavioural tendencies: active facilitation"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "af"
result2 <- alphas(db_proc, c("af_1", "af_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("af_1", "af_2")], na.rm = TRUE)
```

### Intergroup affect tendencies: admiration toward

```{r}
#| label: tbl-desc18
#| tbl-cap: "Descriptive statistics of Intergroup affect tendencies: admiration toward"
#| tbl-cap-location: top

describe_kable(db_proc, c("ad_1", "ad_2"))

```

```{r}
#| collapse: false
# 1. Correlations ppw

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("ad_1", "ad_2"))

```

```{r}
#| label: fig-22
#| fig-cap: "Correlation matrixes of Intergroup affect tendencies: admiration toward"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "ad"
result2 <- alphas(db_proc, c("ad_1", "ad_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("ad_1", "ad_2")], na.rm = TRUE)
```

### Intergroup affect tendencies: contempt toward

```{r}
#| label: tbl-desc19
#| tbl-cap: "Descriptive statistics of Intergroup affect tendencies: contempt toward"
#| tbl-cap-location: top

describe_kable(db_proc, c("co_1", "co_2"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("co_1", "co_2"))

```

```{r}
#| label: fig-23
#| fig-cap: "Correlation matrixes of Intergroup affect tendencies: contempt toward"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "co"
result2 <- alphas(db_proc, c("co_1", "co_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("co_1", "co_2")], na.rm = TRUE)
```

### Intergroup affect tendencies: envy toward

```{r}
#| label: tbl-desc20
#| tbl-cap: "Descriptive statistics of Intergroup affect tendencies: envy toward"
#| tbl-cap-location: top

describe_kable(db_proc, c("en_1", "en_2"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("en_1", "en_2"))

```

```{r}
#| label: fig-24
#| fig-cap: "Correlation matrixes of Intergroup affect tendencies: envy toward"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "en"
result2 <- alphas(db_proc, c("en_1", "en_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("en_1", "en_2")], na.rm = TRUE)
```

### Intergroup affect tendencies: pity toward

```{r}
#| label: tbl-desc21
#| tbl-cap: "Descriptive statistics of Intergroup affect tendencies: pity toward"
#| tbl-cap-location: top

describe_kable(db_proc, c("pi_1", "pi_2"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("pi_1", "pi_2"))

```

```{r}
#| label: fig-25
#| fig-cap: "Correlation matrixes of Intergroup affect tendencies: pity toward"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "pity"
result2 <- alphas(db_proc, c("pi_1", "pi_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("pi_1", "pi_2")], na.rm = TRUE)
```

#### Greedy dispositions

```{r}
#| label: tbl-desc22
#| tbl-cap: "Descriptive statistics of Greedy dispositions"
#| tbl-cap-location: top

describe_kable(db_proc, c("greedy_1", "greedy_2", "greedy_3"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations(db_proc, c("greedy_1", "greedy_2", "greedy_3"))

```

```{r}
#| label: fig-26
#| fig-cap: "Correlation matrixes of Greedy dispositions"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "greedy"
result2 <- alphas(db_proc, c("greedy_1", "greedy_2", "greedy_3"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("greedy_1", "greedy_2", "greedy_3")], na.rm = TRUE)
```

#### Punishment rich

```{r}
#| label: tbl-desc23
#| tbl-cap: "Descriptive statistics of Punishment rich"
#| tbl-cap-location: top

describe_kable(db_proc, c("punish_1", "punish_2", "punish_3"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations(db_proc, c("punish_1", "punish_2", "punish_3"))

```

```{r}
#| label: fig-27
#| fig-cap: "Correlation matrixes of Punishment rich"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "punish"
result2 <- alphas(db_proc, c("punish_1", "punish_2", "punish_3"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("punish_1", "punish_2", "punish_3")], na.rm = TRUE)
```

### Atributtions about poverty

```{r}
#| label: tbl-desc24
#| tbl-cap: "Descriptive statistics of Atributtions about poverty"
#| tbl-cap-location: top

describe_kable(db_proc, c("ex_po_1", "ex_po_2", "in_po_1", "in_po_2"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("ex_po_1", "ex_po_2"))

res3 <- fit_correlations_pairwise(db_proc, c("in_po_1", "in_po_2"))

```

```{r}
#| label: fig-28
#| fig-cap: "Correlation matrixes of Atributtions about poverty: external"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
#| label: fig-29
#| fig-cap: "Correlation matrixes of Atributtions about poverty: internal"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res3, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "ex_atri_po"
result2 <- alphas(db_proc, c("ex_po_1", "ex_po_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("ex_po_1", "ex_po_2")], na.rm = TRUE)
```

```{r}
# 2. Alpha

mi_variable <- "in_atri_po"
result3 <- alphas(db_proc, c("in_po_1", "in_po_2"), mi_variable)

result3$raw_alpha
result3$ord_alpha
result3$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("in_po_1", "in_po_2")], na.rm = TRUE)
```

```{r}
# 3. CFA

# model
model_cfa <- '
  external_atri_po =~ ex_po_1 + ex_po_2
  internal_atri_po =~ in_po_1 + in_po_2
  
'
# estimation 
m4_cfa <- cfa(model = model_cfa, 
              data = db_proc,
              estimator = "DWLS",
              ordered = T,
              std.lv = F) 


```

```{r}
#| label: tbl-7
#| tbl-cap: "Standardized Factor Loadings of Atributtions about poverty"
#| tbl-cap-location: top

cfa_tables(m4_cfa)$loadings_table


```

```{r}
#| label: tbl-8
#| tbl-cap: "Summary fit indices of Atributtions about poverty"
#| tbl-cap-location: top

cfa_tables(m4_cfa)$fit_table

```

### Atributtions about wealth

```{r}
#| label: tbl-desc25
#| tbl-cap: "Descriptive statistics of Atributtions about wealth"
#| tbl-cap-location: top

describe_kable(db_proc, c("ex_we_1", "ex_we_2", "in_we_1", "in_we_2"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("ex_we_1", "ex_we_2"))

res3 <- fit_correlations_pairwise(db_proc, c("in_we_1", "in_we_2"))

```

```{r}
#| label: fig-30
#| fig-cap: "Correlation matrixes of Atributtions about wealth: external"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
#| label: fig-31
#| fig-cap: "Correlation matrixes of Atributtions about wealth: internal"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res3, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "ex_atri_we"
result2 <- alphas(db_proc, c("ex_we_1", "ex_we_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("ex_we_1", "ex_we_2")], na.rm = TRUE)
```

```{r}
# 2. Alpha

mi_variable <- "in_atri_we"
result3 <- alphas(db_proc, c("in_we_1", "in_we_2"), mi_variable)

result3$raw_alpha
result3$ord_alpha
result3$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("in_we_1", "in_we_2")], na.rm = TRUE)
```

```{r}
# 3. CFA

# model
model_cfa <- '
  external_atri_we =~ ex_we_1 + ex_we_2
  internal_atri_we =~ in_we_1 + in_we_2
  
'
# estimation 
m5_cfa <- cfa(model = model_cfa, 
              data = db_proc,
              estimator = "DWLS",
              ordered = T,
              std.lv = F) 


```

```{r}
#| label: tbl-9
#| tbl-cap: "Standardized Factor Loadings of Atributtions about wealth"
#| tbl-cap-location: top

cfa_tables(m5_cfa)$loadings_table


```

```{r}
#| label: tbl-10
#| tbl-cap: "Summary fit indices of Atributtions about wealth"
#| tbl-cap-location: top

cfa_tables(m5_cfa)$fit_table

```

###Thick skin bias

```{r}
#| label: tbl-desc26
#| tbl-cap: "Descriptive statistics of Thick skin bias"
#| tbl-cap-location: top

describe_kable(db_proc, c("sk_1", "sk_2", "sk_3"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations(db_proc, c("sk_1", "sk_2", "sk_3"))


```

```{r}
#| label: fig-32
#| fig-cap: "Correlation matrixes of Thick skin bias"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "sk"
result2 <- alphas(db_proc, c("sk_1", "sk_2", "sk_3"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("sk_1", "sk_2", "sk_3")], na.rm = TRUE)
```

### Deservingness: control poverty

```{r}
#| label: tbl-desc27
#| tbl-cap: "Descriptive statistics of Deservingness: control poverty"
#| tbl-cap-location: top

db_proc$carin_control_2_r <- sjmisc::rec(db_proc$carin_control_2,rec = "rev")

describe_kable(db_proc, c("carin_control_1","carin_control_2_r"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("carin_control_1","carin_control_2_r"))


```

```{r}
#| label: fig-33
#| fig-cap: "Correlation matrixes of Deservingness: control poverty"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "carin_control"
result2 <- alphas(db_proc, c("carin_control_1","carin_control_2_r"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("carin_control_1","carin_control_2_r")], na.rm = TRUE)
```

### Deservingness: attitude poverty

```{r}
#| label: tbl-desc28
#| tbl-cap: "Descriptive statistics of Deservingness: attitude poverty"
#| tbl-cap-location: top

describe_kable(db_proc, c("carin_attitude_1","carin_attitude_2"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("carin_attitude_1","carin_attitude_2"))


```

```{r}
#| label: fig-34
#| fig-cap: "Correlation matrixes of Deservingness: attitude poverty"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "carin_attitude"
result2 <- alphas(db_proc, c("carin_attitude_1","carin_attitude_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("carin_attitude_1","carin_attitude_2")], na.rm = TRUE)
```

### Deservingness: reciprocity poverty

```{r}
#| label: tbl-desc29
#| tbl-cap: "Descriptive statistics of Deservingness: reciprocity poverty"
#| tbl-cap-location: top

describe_kable(db_proc, c("carin_reciprocity_1","carin_reciprocity_2"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("carin_reciprocity_1","carin_reciprocity_2"))


```

```{r}
#| label: fig-35
#| fig-cap: "Correlation matrixes of Deservingness: reciprocity poverty"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "carin_reciprocity"
result2 <- alphas(db_proc, c("carin_reciprocity_1","carin_reciprocity_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("carin_reciprocity_1","carin_reciprocity_2")], na.rm = TRUE)
```

### Deservingness: identity poverty

```{r}
#| label: tbl-desc30
#| tbl-cap: "Descriptive statistics of Deservingness: identity poverty"
#| tbl-cap-location: top

describe_kable(db_proc, c("carin_identity_1","carin_identity_2"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("carin_identity_1","carin_identity_2"))


```

```{r}
#| label: fig-36
#| fig-cap: "Correlation matrixes of Deservingness: identity poverty"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "carin_identity"
result2 <- alphas(db_proc, c("carin_identity_1","carin_identity_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("carin_identity_1","carin_identity_2")], na.rm = TRUE)
```

### Deservingness: need poverty

```{r}
#| label: tbl-desc31
#| tbl-cap: "Descriptive statistics of Deservingness: need poverty"
#| tbl-cap-location: top

describe_kable(db_proc, c("carin_need_1","carin_need_2"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("carin_need_1","carin_need_2"))


```

```{r}
#| label: fig-37
#| fig-cap: "Correlation matrixes of Deservingness: need poverty"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "carin_need"
result2 <- alphas(db_proc, c("carin_need_1","carin_need_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("carin_need_1","carin_need_2")], na.rm = TRUE)
```

## Block 6. Sexuality

### Abuse of social assistance by poor mothers

```{r}
#| label: tbl-desc33
#| tbl-cap: "Descriptive statistics of Abuse of social assistance by poor mothers"
#| tbl-cap-location: top

describe_kable(db_proc, c("wel_abu_1","wel_abu_2"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("wel_abu_1","wel_abu_2"))


```

```{r}
#| label: fig-38
#| fig-cap: "Correlation matrixes of Abuse of social assistance by poor mothers"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "wel_abu"
result2 <- alphas(db_proc, c("wel_abu_1","wel_abu_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("wel_abu_1","wel_abu_2")], na.rm = TRUE)
```

### Paternalistic support for poor mothers

```{r}
#| label: tbl-desc34
#| tbl-cap: "Descriptive statistics of Paternalistic support for poor mothers"
#| tbl-cap-location: top

describe_kable(db_proc, c("wel_pa_1","wel_pa_2"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("wel_pa_1","wel_pa_2"))


```

```{r}
#| label: fig-39
#| fig-cap: "Correlation matrixes of Paternalistic support for poor mothers"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "wel_pa"
result2 <- alphas(db_proc, c("wel_pa_1","wel_pa_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("wel_pa_1","wel_pa_2")], na.rm = TRUE)
```

### Hostile support for poor mothers

```{r}
#| label: tbl-desc35
#| tbl-cap: "Descriptive statistics of Hostile support for poor mothers"
#| tbl-cap-location: top

describe_kable(db_proc, c("wel_ho_1","wel_ho_2"))

```

```{r}
#| collapse: false
# 1. Correlations 

# fit pearson and polychoric
res2 <- fit_correlations_pairwise(db_proc, c("wel_ho_1","wel_ho_2"))


```

```{r}
#| label: fig-40
#| fig-cap: "Correlation matrixes of Hostile support for poor mothers"
#| fig-cap-location: top
#| fig-asp: 1.1
#| out-width: '80%'

#Plot the matrix using corrplot

corr_plots(res2, db_proc, "SOGEDI")

```

```{r}
# 2. Alpha

mi_variable <- "wel_ho"
result2 <- alphas(db_proc, c("wel_ho_1","wel_ho_2"), mi_variable)

result2$raw_alpha
result2$ord_alpha
result2$new_var_summary

db_proc[[mi_variable]] <- rowMeans(db_proc[, c("wel_ho_1","wel_ho_2")], na.rm = TRUE)
```
